### 2021-05-03 newvariant.tex
added a period
removed the

B.M.B. was supported by the Natural Sciences and Engineering Research Council of Canada 
J.D. was supported by the Canadian Institutes of Health Research, 
the The Natural Sciences and Engineering Research Council of Canada, 
and the Michael G. DeGroote Institute for Infectious Disease Research.
J.S.W. was supported by the National Science Foundation (2032082).
The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.

>>>>

B.M.B. was supported by the Natural Sciences and Engineering Research Council of Canada. 
J.D. was supported by the Canadian Institutes of Health Research, 
the Natural Sciences and Engineering Research Council of Canada, 
and the Michael G. DeGroote Institute for Infectious Disease Research.
J.S.W. was supported by the National Science Foundation (2032082).
The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
